Converting LaTeX Legacy R Journal Articles into R Markdown Articles using texor and rebib

### 2023-09-22 texor.Rmd
added the alt-text, used png for figure 1 bc its easier for now and put figures into subdirectory

Pandoc can be used to do the conversion from LaTeX to R Markdown also. However, some pre-processing is necessary to handle special R Journal LaTeX styling. And further post-processing is necessary to handle specific R Journal R Markdown styling. The \CRANpkg{texor} package contains functionality to handle this pre- and post-processing of the document, in a workflow illustrated in Figure \@ref(fig:workflow).

<!-- uses these filters heavily, even for simple tasks like choosing which supporting figures to copy. A `Lua` filter constructs a list of image paths, stores them momentarily and the package uses this data to copy images. However, \CRANpkg{texor} also includes many pre-processing functions that employ regular expressions. This is needed to convert some text and LaTeX commands that are not recognized or handled by Pandoc. -->

```{r workflow, fig.cap="Workflow of the document conversion conducted by texor. (Note: AST is pandoc's abstract syntax tree.)", out.width="100%", fig.align='center', fig.width=4, fig.height=3, layout="l-body", fig.alt="Flow diagram showing original article pre-processed in R passed to pandoc which creates the AST and modifies using many lua filters then passed to pacdoc writer to produce the converted article."}
library(DiagrammeR)
wf <- create_node_df(
        n=8,
        type=c("a", "b", "a", "b", 
               "a", "b", "b", "a"),
        label=c("original article", "pre-processing in R",
                "pre-processed article", "pandoc reader",
                "AST", 
                "modify AST using lua filter",
                "pandoc writer", 
                "converted article"
                ),
        shape="rectangle",
        width=c(1.3, 1.7, 1.9, 1.3, 0.5, 2.3, 1.2, 1.5),
        fillcolor = c("darkseagreen2", "grey85", "darkseagreen2", "grey85", "darkseagreen2", "grey85", "grey85", "darkseagreen2"),
        color = c("black", "grey85", "black", "grey85", "black", "grey85", "grey85", "black"),
        fontcolor="black",
        x=c(1,1,1,1,1,2,1,1),
        y=c(1,2,3,4,5,5,6,6),
        fontsize=14
        )
wf_arrows <- create_edge_df(from = c(1, 2, 3, 4, 5, 6, 5, 7),
                            to = c(2, 3, 4, 5, 6, 5, 7, 8),
                            color="black")
wf_graph <- create_graph(wf, wf_arrows, 
                   directed = TRUE, attr_theme = "tb")
set.seed(7)
render_graph(wf_graph, layout="fr", height=500)
```

@@

```{r alghow, fig.cap="How to write algorithms.", out.width="60%", fig.align='center'}
knitr::include_graphics("alghow.png")
```

>>>>

Pandoc can be used to do the conversion from LaTeX to R Markdown also. However, some pre-processing is necessary to handle special R Journal LaTeX styling. And further post-processing is necessary to handle specific R Journal R Markdown styling. The \CRANpkg{texor} package contains functionality to handle this pre- and post-processing of the document, in a workflow illustrated in Figure \@ref(fig:wf-fig).

```{r workflow, eval=FALSE}
library(DiagrammeR)
wf <- create_node_df(
        n=8,
        type=c("a", "b", "a", "b", 
               "a", "b", "b", "a"),
        label=c("original article", "pre-processing in R",
                "pre-processed article", "pandoc reader",
                "AST", 
                "modify AST using lua filter",
                "pandoc writer", 
                "converted article"
                ),
        shape="rectangle",
        width=c(1.3, 1.7, 1.9, 1.3, 0.5, 2.3, 1.2, 1.5),
        fillcolor = c("darkseagreen2", "grey85", "darkseagreen2", "grey85", "darkseagreen2", "grey85", "grey85", "darkseagreen2"),
        color = c("black", "grey85", "black", "grey85", "black", "grey85", "grey85", "black"),
        fontcolor="black",
        x=c(1,1,1,1,1,2,1,1),
        y=c(1,2,3,4,5,5,6,6),
        fontsize=14
        )
wf_arrows <- create_edge_df(from = c(1, 2, 3, 4, 5, 6, 5, 7),
                            to = c(2, 3, 4, 5, 6, 5, 7, 8),
                            color="black")
wf_graph <- create_graph(wf, wf_arrows, 
                   directed = TRUE, attr_theme = "tb")
set.seed(7)
render_graph(wf_graph, layout="fr", height=500)
```

```{r wf-fig, fig.cap="Workflow of the document conversion conducted by texor. (Note: AST is pandoc's abstract syntax tree.)", out.width="100%", fig.align='center', fig.width=3, fig.height=5, layout="l-body", fig.alt="Flow diagram showing original article pre-processed in R passed to pandoc which creates the AST and modifies using many lua filters then passed to pacdoc writer to produce the converted article."}
knitr::include_graphics("figures/wf.png")
```

@@

```{r alghow, fig.cap="How to write algorithms.", out.width="60%", fig.align='center', fig.alt="Illustration of an algorithm starting with Data and Result, followed by a while, and an if/else block."}
knitr::include_graphics("figures/alghow.png")
```

### 2023-09-22 texor.tex
added the alt-text, used png for figure 1 bc its easier for now and put figures into subdirectory

Pandoc can be used to do the conversion from LaTeX to R Markdown also. However, some pre-processing is necessary to handle special R Journal LaTeX styling. And further post-processing is necessary to handle specific R Journal R Markdown styling. The \CRANpkg{texor} package contains functionality to handle this pre- and post-processing of the document, in a workflow illustrated in Figure \ref{fig:workflow}.

@@

{\centering \includegraphics[width=1\linewidth]{texor_files/figure-latex/workflow-1}

@@

\caption{Workflow of the document conversion conducted by texor. (Note: AST is pandoc's abstract syntax tree.)}\label{fig:workflow}
\end{figure}

@@

{\centering \includegraphics[width=0.6\linewidth]{alghow}

>>>>

Pandoc can be used to do the conversion from LaTeX to R Markdown also. However, some pre-processing is necessary to handle special R Journal LaTeX styling. And further post-processing is necessary to handle specific R Journal R Markdown styling. The \CRANpkg{texor} package contains functionality to handle this pre- and post-processing of the document, in a workflow illustrated in Figure \ref{fig:wf-fig}.

@@

{\centering \includegraphics[width=1\linewidth]{figures/wf}

@@

\caption{Workflow of the document conversion conducted by texor. (Note: AST is pandoc's abstract syntax tree.)}\label{fig:wf-fig}
\end{figure}

@@

{\centering \includegraphics[width=0.6\linewidth]{figures/alghow}
